One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-09-21 manuscript/manuscript.tex
adding missing reference and bug: textt --> texttt

The ODT model formulation is somewhat complex and is difficult to cleanly separate from its implementation. For instance, while the triplet map can be represented mathmatically, it is usually implemented as we described previously. That description assumed an adaptive grid with variable cell sizes. Alternative formulations are used for fixed grids. Furthermore, the model itself is complex and difficult to implement. These challenges present barriers for practitioners who wish to use the model. The code presented aims to reduce these barriers by providing an open-source, well-documented code that can be used directly, or modified to suit particular research aims. New research questions that could be persued include soot-flame-radiation-chemsitry interactions, multi-phase reacting flows (such as diesel sprays) using Lagrangian particles, and coupled near-wall heat and momentum transfer, to name a few. The code presented has been demonstrated to be extensible to such systems. These extensions are facilitated by the object-oriented structure, including the domain variables. For example, the code has be extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \textt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.

>>>>

The ODT model formulation is somewhat complex and is difficult to cleanly separate from its implementation. For instance, while the triplet map can be represented mathmatically, it is usually implemented as we described previously. That description assumed an adaptive grid with variable cell sizes. Alternative formulations are used for fixed grids. Furthermore, the model itself is complex and difficult to implement. These challenges present barriers for practitioners who wish to use the model. The code presented aims to reduce these barriers by providing an open-source, well-documented code that can be used directly, or modified to suit particular research aims. New research questions that could be persued include soot-flame-radiation-chemsitry interactions, multi-phase reacting flows (such as diesel sprays) using Lagrangian particles, and coupled near-wall heat and momentum transfer, to name a few. The code presented has been demonstrated to be extensible to such systems. These extensions are facilitated by the object-oriented structure, including the domain variables. For example, the code has be extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \texttt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.
